Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-05-27 ms.tex
added plots of the Mg triplet analysis compared with some HIGHRES models.

\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/nad_spec.pdf}
\caption{Example spectrum of \shStar\ near the Na D line.
There are many bad pixels.}\label{fig:naDline}
\end{centering}
\end{figure}

>>>>

\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/nad_spec.pdf}
\caption{Example spectrum of \shStar\ near the Na D$_1$ and D$_2$ lines (black vertical lines).
There are many bad pixels.}\label{fig:naDline}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec_interp.pdf}
\includegraphics[width=0.45\textwidth]{images/subaru/Mg_triplet_spec.pdf}
\caption{Example spectrum of \shStar\ near the Mg triplet.
First, the points above 2.0 are flagged as bad pixels and interpolated over.
Second, a convolution kernel is applied and the spectrum is compared to HIGHRES models.}\label{fig:mgTriplet}
\end{centering}
\end{figure}
